### 2024-12-03 introduction.tex
Stage work on drafting Background parts, minor change in introduction.tex
Fixed pdf generation, citation

\chapter[Introduction]{Chapter 1 Introduction}
\label{chap:1}

@@

Theorem proving is another widely used formal analysis technique. It does not suffer from the limitations of state space size as model checking does, which allows the analysis of larger and more complex systems. Furthermore, theorem provers use very expressive logics, like first-order or higher-order logics, which enable the study of a wider range of systems without the restrictions that often come with modeling. The most prominent provers are HOL4 \cite{slind2008brief}, HOL Light \cite{hol_light}, Coq \cite{bertot2013interactive}, and Isabelle/HOL \cite{isabelle_hol}, all broadly used in the community.

>>>>

\chapter{Introduction}
\label{intro}

@@

Theorem proving is another widely used formal analysis technique. It does not suffer from the limitations of state space size as model checking does, which allows the analysis of larger and more complex systems. Furthermore, theorem provers use very expressive logics, like first-order or higher-order logics, which enable the study of a wider range of systems without the restrictions that often come with modeling. The most prominent provers are HOL4 \cite{slind2008brief}, HOL Light \cite{hollight}, Coq \cite{bertot2013interactive}, and Isabelle/HOL \cite{isabelle}, all broadly used in the community.
